Methodology for Assessing the State of the Practice for Domain X

### 2020-09-08 StateOfPractice/Methodology/Methodology.tex
updated Domain Analysis section of Methodology

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be reviewed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be completed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed - go over how to clean this up in meeting, or through an issue}
\item Measure using ``shallow'' measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be reviewed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be reviewed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item With short list:
\begin{enumerate}
\item Survey developers (\href{run:Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{run:User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

@@

\section{Domain Analysis} \label{SecDomainAnalysis}

Commonality analysis.  Follow as for mesh generator (likely with less detail).
Final result will be tables of commonalities, variabilities and parameters of
variation.

Commonality analysis document Steps:
\begin{enumerate}
\item Introduction
\item Overview of Domain
\item Add Commonalities - Split into simulation, input, output, and
  nonfunctional requirements
\item Add Variabilities - Split into simulation, input, output, system
  constraints, and nonfunctional requirements
\item Add Parameters of Variation - Split into simulation, input, output, system
  constraints, and nonfunctional requirements
\item Add Terminology, Definitions, Acronyms
\end{enumerate}

Commonality analysis for Lattice Boltzmann Solvers can be found
\href{run:../Peter-Notes/Commonality-Analysis-LB-Systems.pdf}{here}.

>>>>

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed; should I remove section 2 from above and just link to ../OverallResearchProposal/ObjectivesAndResearchQuestions.pdf?, move the doc to this folder?}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be reviewed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be reviewed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed - go over how to clean this up in meeting, or through an issue}
\item Measure using ``shallow'' measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be reviewed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be reviewed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item With short list:
\begin{enumerate}
\item Survey developers (\href{run:Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{run:User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

@@

\section{Domain Analysis} \label{SecDomainAnalysis}
The domain analysis consists of a commonality analysis of the software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. The final result of the analysis will be tables of commonalities, variabilities and parameters of variation.

\noindent Steps to produce a commonality analysis:
\begin{enumerate}
\item Write an Introduction
\item Write the Overview of Domain
\item List Commonalities - Split into sections for the simulation step, input information, output information, and nonfunctional requirements
\item List Variabilities - Split into sections for the simulation step, input information, output information, and nonfunctional requirements
\item List Parameters of Variation - Split into sections for the simulation step, input information, output information, system constraints, and nonfunctional requirements
\item Add Terminology, Definitions, Acronyms
\end{enumerate}

A sample commonality analysis for Lattice Boltzmann Solvers can be found
\href{run:../Peter-Notes/Commonality-Analysis-LB-Systems.pdf}{here}.
